---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE
)

wd <- rprojroot::find_rstudio_root_file()
knitr::opts_knit$set(root.dir = wd)
```


## Package Review

*Please check off boxes as applicable, and elaborate in comments below.  Your
review is not limited to these topics, as described in the reviewer guide*

- [x] As the reviewer I confirm that there are no conflicts of interest for me
to review this work (such as being a major contributor to the software).

#### Documentation

The package includes all the following forms of documentation:

- [x] **A statement of need** clearly stating problems the software is designed to solve and its target audience in README
- [x] **Installation instructions:** for the development version of package and any non-standard dependencies in README
- [x] **Vignette(s)** demonstrating major functionality that runs successfully locally
- [x] **Function Documentation:** for all exported functions in R help
- [x] **Examples** for all exported functions in R Help that run successfully locally
- [x] **Community guidelines** including contribution guidelines in the README or CONTRIBUTING, and `URL`, `Maintainer` and `BugReports` fields in DESCRIPTION


#### Functionality

- [x] **Installation:** Installation succeeds as documented.
- [x] **Functionality:** Any functional claims of the software been confirmed.
- [x] **Performance:** Any performance claims of the software been confirmed.
- [x] **Automated tests:** Unit tests cover essential functions of the package
   and a reasonable range of inputs and conditions. All tests pass on the local machine.
- [x] **Packaging guidelines**: The package conforms to the rOpenSci packaging guidelines

#### Final approval (post-review)

- [ ] **The author has responded to my review and made changes to my satisfaction. I recommend approving this package.**

Estimated hours spent reviewing: 8

---

### Review Comments

This package is a tool for generating fake data. Users can create fake data of a
given type by using functions that start with `ch_`. For example,
`ch_credit_card_number()` creates a fake credit card number or 
`ch_name(n = 4, locale = "fr_FR")` creates four fake French-sounding names. 
Applications for the package include education (creating fake datasets for
students), statistical simulation, software testing, and perhaps anonymization.

Charlatan is modeled after Python's Faker library which in turn draws
inspiration from PHP Faker, Ruby Faker and Perl Faker. (Unfortunately, the
name Faker has been taken on CRAN.) (It is also worth noting that 
[wakefield](https://github.com/trinker/wakefield) is another R package for fake-data.
Wakefield provides *data-frames* of fake data, whereas this package mainly
provides *vectors* of fake data.)

Overall, this package is well designed and well structured, although I found few
bugs and inconsistencies while reviewing it.

This package uses the R6 object system to create classes of data-generators.
(Presumably, using objects and methods made porting the code from Python rather
straightforward.) The base class is the `BaseGenerator` class. All other
generators inherit from this class. Therefore, I'll review the code by visiting
each of the generators in turn.

#### BaseProvider

`BaseProvider` contains methods for generating random digits, random letters,
and populating templates with random strings.

```{r}
library(charlatan)
bp <- BaseProvider$new()
bp

bp$random_digit()
bp$numerify("I have ## friends")
```

This package makes extensive use of the `sample()` function. This function has a
flawed default behavior: It expands integers into ranges. Thus, `sample(10, 1)`
is the same as `sample(1:10, 1)`. This package's `BaseProvider$random_element()`
method inherits this flaw.

```{r}
set.seed(22)
bp$random_element(10)
```

Perhaps, `x[sample(seq_along(x), 1)]`, which would sample from a
sequence of item positions, would be a better implementation for this method.


The method `random_int()` has the signature:

```{r}
str(args(bp$random_int))
```

It can never generate the maximum value, and this fact isn't noted anywhere. 

```{r}
set.seed(22)
range(replicate(bp$random_int(min = 0, max = 99), n = 100000))
```

~~It's not clear whether this is intentional or an oversight, but it's the kind
of weird detail that should be noted.~~ On further consideration, this is
probably a bug because the DOI-generators uses the function with min = 0 and max
= 9999.

I'm curious why the digit-or-blank generators don't just sample from a larger
set. The code for `random_digit_not_null_or_empty()` means that half of the
generated items should be` ""`.

```{r}
bp$random_digit_not_null_or_empty

# Why not sample with this instead?
bp$random_element(c(1:9, ""))
```



#### NumericsProvider

This class generates random numbers. This class demonstrates nice features of
the R6-based design: 

1. grouping similar functionality into a cohesive object
2. providing a logical extension point for other kinds of number generators

```{r}
np <- NumericsProvider$new()
np
```

This class powers the various random number generators in the package.
The functions `ch_integer()`, `ch_double()`, `ch_unif()`, etc.
actually just generate one-off `NumericsProvider` objects and call a method.

```{r}
ch_norm
```

The package rightly calls upon R's built-in number generators (`rnorm`, `runif`,
`rbeta`, etc.) for almost all of the number generators. It uses different 
defaults for the uniform distribution than R, but uses the same defaults as R
for the others. 

```{r}
args(runif)
args(NumericsProvider$new()$unif)
```

Here I think the package should follow R's defaults and take advantage of what
the user may already know about the `r*` functions.

The `integer()` method doesn't defer to R, but instead uses `sample()`. By
default, `sample()` does not sample with replacement so 
`NumericsProvider$new()$integer()` and `ch_integer()` can behave in unexpected
ways.

```{r, error = TRUE}
ch_integer(n = 10000, min = 1, max = 1000)
```

It is also odd that the `random_int()` and `integer()` use different techniques
for generating random integers.



#### PersonProvider

This class implements the package's impressive and fun random name generator
feature. It can generator locale-specific names. It has one method: `render()`. 
This class powers the `ch_name()` function.

```{r}
set.seed(100)
person <- PersonProvider$new()
person$render()
person$render()
person$render()

ch_name(4)
```

As the example above shows, the names can vary in format. (Sometimes there
is a blank first name --- this might be a bug.)

This function works by randomly selecting a name format, and populating the
format with random names/affixes. 

```{r}
# Formats
person$formats

# Possible slot fillers
str(person$person)
```

The package's locale-specificity is just a matter of selecting the appropriate 
formats and slot fillers for a locale. This implementation is a clean design
win.

The locale-specific names are stored as variables in the package's namespace,
and they are stored in R scripts. Thus, there are .R files that contain vectors
with thousands of names. 

```{r}
r_dir <- rprojroot::find_rstudio_root_file("R/")
list.files(r_dir, "person-provider-")
```

I wonder if using a `data/` folder would be a cleaner
way to separate code and package data.

The documentation for `ch_name` under-reports the supported locales. For
example, Spanish is supported but this Spanish support is not documented.

There is a bug in how double last names (as in Spanish) are generated.

```{r}
set.seed(103)
spanish <- PersonProvider$new(locale = "es_ES")

# Double last names are common in Spanish
spanish$formats

# The two last names should be different
spanish$render()
spanish$render()
```

This is a problem with `whisker::render()`. The following code tweaks the
package internals for debugging. It generates four different last names but
whisker recycles the first.

```{r}
pluck_names <- charlatan:::pluck_names

fmt <- "{{last_name}} {{last_name}} {{last_name}} {{last_name}}"
dat <- lapply(
  spanish$person[pluck_names(fmt, spanish$person)], 
  sample, 
  size = 1)

str(dat)
whisker::whisker.render(fmt, data = dat)
```

#### ColorProvider

This class generates colors. 

Its hex-color generator users the `random_int()` method to choose a number 
between 1 and 16777215. The above noted behavior means it will never generate 
\#ffffff or, I think, \#000000. 

```{r}
cp <- ColorProvider$new()
cp$color_name()
cp$safe_color_name()

# Some locale sensitivity for color names, but not safe ones
cp2 <- ColorProvider$new(locale = "uk_UA")
cp2$color_name()
cp2$safe_color_name()

set.seed(26)
cp$hex_color()
```

It pads zeros onto strings less than 6 characters to create the familiar six- 
digit format. But padding is done on the right side, so it will never generate 
"#0000ff". It also counts character length after appending the the pound sign,
so the above example shows an incorrect hex color.

~~I think using `sprintf("#%06x", ...)` would fix these problems.~~ Actually,
I discovered `grDevices::rgb()` while reading about the `colors()` in a later
comment. That should power the implementation.

```{r}
rgb(0, 0, 0, maxColorValue = 255)
rgb(255, 255, 255, maxColorValue = 255)

sample_col <- function() sample(0:255, 1)
rgb(sample_col(), sample_col(), sample_col(), maxColorValue = 255)
```

A similar strategy underlies the `safe_hex_color()` method, so that has the same
flaws. Plus, something mysterious happens sometimes: 

```{r}
set.seed(26)
cp$safe_hex_color()
```

For this method I think generating three separate hex digits and duplicating
them and concatenating them would be a cleaner implementation. I also find
[conflicting information](http://websafecolors.info/color-chart) about which
colors are "safe" -- is this method's definition of safe colors standard?

`rbg_color()` calls the `hex_color()` method, so it will inherit that function's 
bugs. Plus, sometimes I get an error.

```{r, error = TRUE}
set.seed(133)
colors <- replicate(n = 1000, cp$rgb_color())
```

R has its own family of accepted color names, so those might a natural
extension point.

```{r}
sample(colors(), 3)
```


#### CoordinateProvider

CoordinateProviders does what it says. It powers `ch_lat()`, `ch_lon()`,
`ch_position()`. Notably, it does not inherit from the BaseProvider class.

```{r}
cp <- CoordinateProvider$new()
CoordinateProvider

cp$lat()
cp$lon()
cp$position()
```

It can generate coordinates within a boundary box. The box is not checked, so
users can get invalid coordinates as a result.

```{r}
# Specify a bad box
cp$position(c(-12000, 0, 0, 30000))
```


#### CreditCardProvider

This class looks good but there is some commented out Python/R code in place. It
looks like the class produces legitimate credit card numbers (i.e., they pass an
appropriate checksum that real credit card numbers have). This detail highlights
an important use case for this package: Generating fake data for testing code,
as one could test some credit-card-validating function with this package.

#### DateTimeProvider

This class powers `ch_timezone()`, `ch_unix_time()`, and `ch_date_time()`. It
is not documented that the date-times are integers converted to POSIX times, so
they are all after 1970. The file also features some commented out Python code.

```{r}
DateTimeProvider$new()$unix_time()
DateTimeProvider$new()$date_time()
```

There is a typo in `century()` method, so it always errors.

```{r}
body(DateTimeProvider$new()$century)
```

#### TaxonomyProvider

This class randomly samples from prepackaged genus/species names. The basis for 
the random genus/species names are well detailed in the hidden 
`?TaxonomyProvider` but not in the user-facing `?taxonomy` page. Now that 
Roxygen2 supports new `@inherit` and `@inheritSection fun title` directives, I
suggest that the user-facing page include this documentation. 

```{r}
set.seed(22)
TaxonomyProvider$new()$genus()
TaxonomyProvider$new()$epithet()

# A species just genus() + epithet()
set.seed(22)
TaxonomyProvider$new()$species()
```


#### Do-one-thing generators

##### CurrencyProvider

This class randomly samples a vector of currency abbreviations.

##### DOIProvider

This classes main job is to randomly select DOI formats, then populate those
formats with characters/integers. This class does not use its inherited
`random_int()` method to generate the integers, but it should.

##### JobProvider

The class produces occupation titles, using the same locale-specificity covered 
earlier. It just randomly samples occupations from a vector with each locale's
occupation names.

```{r}
set.seed(36)
JobProvider$new(locale = "fr_FR")$render()
ch_job(n = 3)
```

##### PhoneNumberProvider

This class randomly selects a format and then populates that format with digits.

```{r}
head(PhoneNumberProvider$new()$formats, 3)
PhoneNumberProvider$new()$render()
ch_phone_number(4)
```

##### SequenceProvider

This class generates gene sequences by sampling letters and concatenating them.

I feel the user-facing function should be named `ch_gene_sequence()`, not
`ch_sequence()`



#### FraudsterClient

This class wraps all the `ch_` functions into a single object for 
general-purpose fake data generation in a given locale. Because locales are not 
uniformly supported, this can lead to errors. Also, the `name()` method ignores
locale when it can support it.

```{r, error = TRUE}
y <- fraudster(locale = "fr_FR")
y

y$job()
y$color_name()
y$name()
```

#### Unfinished providers

I didn't closely review the code for these classes, as they appear to be
unfinished and are not user-facing like the other ones. I am documenting them
here for completeness.

The package contains exported, in-progress code for generating addresses with
`AddressProvider`. There is no `ch_address`. 

It also contains `company_provider()` which is exported but not documented
and not linked to any `ch_` functions. It has a different R6 design and naming
scheme than other classes. This one looks like a lot of fun.

```{r}
# I think the same whisker::render() bug is happening here
set.seed(27)
company_provider()$company()
company_provider()$company()
company_provider()$company()

company_provider()$bs()
company_provider()$bs()

company_provider()$catch_phrase()
company_provider()$catch_phrase()
```

`MissingProvider` provides a method to inject NA values into a vector. There is
no user-facing function (something like `ch_missing`) for this class).
Nevertheless, it's odd that the _n_ missing values it generates for a vector
overwrite the first _n_ values.

```{r}
set.seed(10)
MissingDataProvider$new()$make_missing(letters)
```

I feel like it should randomly determine _n_, `sample()` _n_ position indices,
and make the elements in those positions  NA, so that the NAs are scattered
throughout the vector.


#### `ch_generate()`

This function creates a data-frame of (en_US) fake data.

```{r}
ch_generate("name", "job", n = 4)
```

The standard error for a bad field name is:

```{r, error = TRUE}
ch_generate("badname", n = 2)
```

A better error might say, `see ?ch_generate` or print out the `all_choices`
vector.

`ch_generate("hex_color")` does not work, although the documentations claims to
support it.

The documentation for the `n` argument says "any (integer) number of things to 
get, 1 to inifinity". I would recommend just saying any non-negative integer.
This applies to every documentation page as well.

The documentation for `...` should also say that `name`, `job`, and
`phone_number` columns are created by default if nothing is specified.


#### Other comments

`parse_eval()` should move to zzz.R, where the rest of the utility functions 
live. Personally, I would avoid using this function by structuring all the data
into a nested list so that items can be retrieved with `data[[locale_name]]`
instead of using `parse_eval()` to create-then-evaluate a variable name.

Some functions have `return()`; some do not.

The `random_digit_not_null` method in the BaseGenerator is better named
`random_digit_not_zero`.

The unit test for colors and safe colors should check that the generated colors
meets the color and safe-color formats.

There are only unit-tests for the colors, coordinates, credit cards, currency 
and jobs. I would suggest adding tests for the functions I've described bugs in.

